---
title: "Introduction to the Reproducible Open Coding Kit (ROCK)"
author: "Gjalt-Jorn Peters & Szilvia Zörgő"
date: "`r Sys.Date()`"
output:
  pdf_document:
    toc: false
  rmarkdown::html_vignette:
    toc: true
vignette: >
  %\VignetteIndexEntry{Introduction to the Reproducible Open Coding Kit (ROCK)}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
  %\usepackage[utf8]{inputenc}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The Reproducible Open Coding Kit (ROCK) was developed to facilitate reproducible and open coding, specifically geared towards qualitative research methods. It was designed to be a standard that realized coded qualitative data that is simultaneously human- and machine-readable, similar to the spirit of Markdown and YAML.

To code something with the ROCK, add the code to the line your want to code, in between two pairs of square brackets:

```
Some example text,
and some more.       [[look_a_code]]
And the end.
```

THe `{rock}` package can parse sources like this, and then allows you to do what you can do with conventional (often proprietary) software for qualitative analysis. For example, it can prettify the source. To illustrate this, we first store the contents as a ROCK source:

```{r}
exampleROCK <-
  rock::as.rock_source(c(
    "Some example text,",
    "and some more.       [[look_a_code]]",
    "And the end."));
```

Then we prettify it:

```{r, results='asis'}
rock::prettify_source(
  exampleROCK
);
```

A more extensive introduction is available in the blog post at [https://sciencer.eu/posts/2024-12-rock-basics.html](https://sciencer.eu/posts/2024-12-rock-basics.html). IN addition, the ROCK website, [https://rock.science](https://rock.science), links to a number of tutorials and workshops.
